STR: Seasonal-Trend decomposition using Regression

### 2021-04-02 str_ijds.Rmd
Ready to resubmit

Note that the model subsumes the case of a linear trend, obtained when $\sigma_L^2=0$.

@@

Again, by setting the smoothing parameters to zero, some simple special cases are obtained. Setting $\sigma_i$ to zero eliminates the $i$th seasonal component (as it will be equal to zero); setting the variance in the time direction to zero causes the seasonal component to be periodic; setting the variance in the time-season direction to zero causes ????.

>>>>

Note that the model subsumes the case of a linear trend, obtained when $\sigma_L=0$ (making the trend's second derivatives equal to zero).

@@

Again, by setting the smoothing parameters to zero, some simple special cases are obtained. Setting the variance of the seasonal component in the time-seasonal direction to zero causes the seasonal component to be periodic. By setting both trend and time-seasonal variances to zero we effectively force our model to have a linear trend with seasonal dummies. Setting the variance of the second derivatives of the seasonal component in the time direction to zero alone makes changes in the seasonal component linear over time, but does not preclude the seasonal pattern from changing.

### 2021-04-02 str_ijds.tex
Ready to resubmit

Note that the model subsumes the case of a linear trend, obtained when \(\sigma_L^2=0\).

@@

Again, by setting the smoothing parameters to zero, some simple special cases are obtained.
Setting \(\sigma_L\) to zero makes trend linear (as it makes trend's second derivatives equal to zero). On the other hand, setting the variance of the seasonal component in the time-seasonal direction to zero causes the seasonal component to be periodic. By setting both variances to zero we effectively force our model to have a linear trend with seasonal dummies.
Although, setting the variance of the second derivatives of the seasonal component in the time direction to zero alone makes changes in the seasonal component linear over time, but does not preclude the seasonal pattern from changing.

@@

\caption{\label{tab:cbetable}RMSE over 100 simulations for each DGP and value of $\gamma$. Bold values indicate results that are significantly different from the STR values.}
\centering
\begin{tabular}[t]{rlrrrr}
\toprule
$\gamma$ & Method & Trend RMSE & Weekly RMSE & Yearly RMSE & Remainder RMSE\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Stochastic DGP}}\\
\hspace{1em}0.2 & STL & \textbf{0.0808} & \textbf{0.0564} & \textbf{0.1267} & \textbf{0.1525}\\
\hspace{1em}0.2 & TBATS & \textbf{0.1849} & \textbf{0.0173} & \textbf{0.1785} & \textbf{0.0582}\\
\hspace{1em}0.2 & STR & 0.0183 & 0.0149 & 0.0475 & 0.0515\\
\midrule
\hspace{1em}0.4 & STL & \textbf{0.0798} & \textbf{0.1148} & \textbf{0.2299} & \textbf{0.2659}\\
\hspace{1em}0.4 & TBATS & \textbf{0.3435} & \textbf{0.0344} & \textbf{0.3310} & \textbf{0.1227}\\
\hspace{1em}0.4 & STR & 0.0320 & 0.0301 & 0.0778 & 0.0876\\
\midrule
\hspace{1em}0.6 & STL & \textbf{0.0846} & \textbf{0.1717} & \textbf{0.3388} & \textbf{0.3884}\\
\hspace{1em}0.6 & TBATS & \textbf{0.5107} & \textbf{0.0508} & \textbf{0.4983} & \textbf{0.1648}\\
\hspace{1em}0.6 & STR & 0.0523 & 0.0438 & 0.1136 & 0.1273\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Deterministic GDP}}\\
\hspace{1em}0.2 & STL & \textbf{0.1272} & \textbf{0.0575} & \textbf{0.1402} & \textbf{0.1748}\\
\hspace{1em}0.2 & TBATS & \textbf{0.2304} & \textbf{0.0166} & \textbf{0.2259} & \textbf{0.0803}\\
\hspace{1em}0.2 & STR & 0.0851 & 0.0147 & 0.1000 & 0.0607\\
\midrule
\hspace{1em}0.4 & STL & \textbf{0.1135} & \textbf{0.1147} & \textbf{0.2374} & \textbf{0.2757}\\
\hspace{1em}0.4 & TBATS & \textbf{0.3393} & \textbf{0.0340} & \textbf{0.3294} & \textbf{0.1153}\\
\hspace{1em}0.4 & STR & 0.0584 & 0.0306 & 0.0937 & 0.0929\\
\midrule
\hspace{1em}0.6 & STL & \textbf{0.1439} & \textbf{0.1714} & \textbf{0.3427} & \textbf{0.4018}\\
\hspace{1em}0.6 & TBATS & \textbf{0.5444} & \textbf{0.0509} & \textbf{0.5298} & \textbf{0.1709}\\
\hspace{1em}0.6 & STR & 0.0757 & 0.0436 & 0.1691 & 0.1709\\
\bottomrule
\end{tabular}
\end{table}

>>>>

Note that the model subsumes the case of a linear trend, obtained when \(\sigma_L=0\) (making the trend's second derivatives equal to zero).

@@

Again, by setting the smoothing parameters to zero, some simple special cases are obtained. Setting the variance of the seasonal component in the time-seasonal direction to zero causes the seasonal component to be periodic. By setting both trend and time-seasonal variances to zero we effectively force our model to have a linear trend with seasonal dummies. Setting the variance of the second derivatives of the seasonal component in the time direction to zero alone makes changes in the seasonal component linear over time, but does not preclude the seasonal pattern from changing.

@@

\caption{\label{tab:cbetable}RMSE over 100 simulations for each DGP and value of $\gamma$. Bold values indicate results that are significantly different from the STR values.}
\centering
\begin{tabular}[t]{rlrrrr}
\toprule
$\gamma$ & Method & Trend RMSE & Weekly RMSE & Yearly RMSE & Remainder RMSE\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Stochastic DGP}}\\
\hspace{1em}0.2 & STL & \textbf{0.0808} & \textbf{0.0564} & \textbf{0.1267} & \textbf{0.1525}\\
\hspace{1em}0.2 & TBATS & \textbf{0.1830} & \textbf{0.0174} & \textbf{0.1767} & \textbf{0.0566}\\
\hspace{1em}0.2 & STR & 0.0183 & 0.0149 & 0.0475 & 0.0515\\
\midrule
\hspace{1em}0.4 & STL & \textbf{0.0798} & \textbf{0.1148} & \textbf{0.2299} & \textbf{0.2659}\\
\hspace{1em}0.4 & TBATS & \textbf{0.3435} & \textbf{0.0344} & \textbf{0.3310} & \textbf{0.1227}\\
\hspace{1em}0.4 & STR & 0.0320 & 0.0301 & 0.0778 & 0.0876\\
\midrule
\hspace{1em}0.6 & STL & \textbf{0.0846} & \textbf{0.1717} & \textbf{0.3388} & \textbf{0.3884}\\
\hspace{1em}0.6 & TBATS & \textbf{0.5107} & \textbf{0.0508} & \textbf{0.4983} & \textbf{0.1648}\\
\hspace{1em}0.6 & STR & 0.0523 & 0.0438 & 0.1136 & 0.1273\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Deterministic GDP}}\\
\hspace{1em}0.2 & STL & \textbf{0.1272} & \textbf{0.0575} & \textbf{0.1402} & \textbf{0.1748}\\
\hspace{1em}0.2 & TBATS & \textbf{0.2304} & \textbf{0.0166} & \textbf{0.2259} & \textbf{0.0803}\\
\hspace{1em}0.2 & STR & 0.0851 & 0.0147 & 0.1000 & 0.0607\\
\midrule
\hspace{1em}0.4 & STL & \textbf{0.1135} & \textbf{0.1147} & \textbf{0.2374} & \textbf{0.2757}\\
\hspace{1em}0.4 & TBATS & \textbf{0.3393} & \textbf{0.0340} & \textbf{0.3294} & \textbf{0.1153}\\
\hspace{1em}0.4 & STR & 0.0584 & 0.0306 & 0.0937 & 0.0929\\
\midrule
\hspace{1em}0.6 & STL & \textbf{0.1439} & \textbf{0.1714} & \textbf{0.3427} & \textbf{0.4018}\\
\hspace{1em}0.6 & TBATS & \textbf{0.5444} & \textbf{0.0509} & \textbf{0.5298} & \textbf{0.1709}\\
\hspace{1em}0.6 & STR & 0.0757 & 0.0436 & 0.1691 & 0.1709\\
\bottomrule
\end{tabular}
\end{table}
